\chapter{Datasets}

Website for data import, wrangling and visualization in R: \href{http://www.computerworld.com/article/2921176/business-intelligence/great-r-packages-for-data-import-wrangling-visualization.html}{computerworld}.\\

\section{Healthcare}
Key website for health data: \href{https://www.nlm.nih.gov/hsrinfo/datasites.html}{HSRIC}.\\
\subsection{Behavioral Risk Factor}
The data can be downloaded as csv file:
\begin{enumerate}
\item \href{https://chronicdata.cdc.gov/api/views/xuxn-8kju/rows.csv?accessType=DOWNLOAD}{life-quality}. Health related quality of life survey.
\item \href{https://chronicdata.cdc.gov/api/views/hn4x-zwk7/rows.csv?accessType=DOWNLOAD}{nutrition}. Very recent data.
\item \href{ftp://ftp.cdc.gov/pub/Health_Statistics/NCHS/Datasets/CHDI/chsi_dataset.zip}{indicators}. This is a zipped file. 
\end{enumerate}

\textbf{Note:} There is metadata (json) for the above datasets.

I'm not going to want to save this data to my hard drive, at least not initially. So I can use R packages to download directly from the website.

Example:
\begin{verbatim}
library(data.table)
mydat <- fread("https://website.url.here")
\end{verbatim}

\subsection{Healthcare Spending}

\begin{enumerate}
\item \href{https://meps.ahrq.gov/mepsweb/data_stats/download_data_files.jsp}{raw data}. This is in json.
\item \href{https://aspe.hhs.gov/system/files/aspe-files/253321/dec2016statebystate.xlsx}{ACA}. This is xlsx file.
\item \href{http://www.commonwealthfund.org/~/media/Files/2017%20State%20Scorecard/Public%20Use%20File/2017_state_scorecard_public_use_data_file.xlsx}{state performance}. This is also xlsx file. 
\end{enumerate}

\section{Video Gaming}
Changing topics to video gaming, but don't want to lose the information above.

I first download the available excel file for game rating, and convert to csv. Next, I need the sales data for these games.

Below are the datasets including game ratings and unit sales. Furthermore, I have additional datasets for franchise information and best-selling video game based on money earned and not units sold. This is a significantly smaller dataset.

\begin{enumerate}
\item \href{http://www.gamerankings.com/sites/1188-ign/index.html?platform=116}{game rankings}
\item \href{http://www.vgchartz.com/gamedb/?name=&publisher=&platform=&genre=&minSales=0&results=1000}{game database}
\item \href{https://www.dropbox.com/s/09sh15zbtwg9eu3/gamedata.xlsx}{xlsx game ranking}
\item \href{http://vgsales.wikia.com/wiki/Video_Game_Sales_Wiki}{vg wiki}
  \begin{enumerate}
  \item \href{http://vgsales.wikia.com/wiki/Best_selling_game_franchises}{highest franchises}
  \item \href{http://vgsales.wikia.com/wiki/Best_selling_games_worldwide}{best-selling vg}
  \item \href{http://vgsales.wikia.com/wiki/Most_expensive_games}{most expensive vg}
  \item \href{http://vgsales.wikia.com/wiki/Pok%C3%A9mon#Pok.C3.A9mon_sales_figure}{pokemon}
  \item \href{http://vgsales.wikia.com/wiki/Sonic}{sonic the hedgehog}
  \item \href{http://vgsales.wikia.com/wiki/Mario}{mario}
  \item \href{http://vgsales.wikia.com/wiki/Grand_Theft_Auto}{gta: grand theft auto}
  \item \href{http://vgsales.wikia.com/wiki/Halo}{halo}
  \end{enumerate}
\end{enumerate}

